TacticToe: Learning the Game of Tactics

### 2018-02-08 tactictoe_jv.tex
Work a little more on section 1

Two ways of representing a formulas.
Definition of a tactic in \holfour. In this research, we will take the definition
that a tactic takes a goal and returns a list of goals.
Input of the prediction: goal
If a tactic produces no goals then its input goal is solved.
Define tactical etc maybe import graphic that explain how tactic works form the
presentations.

mention proof obligations (use this word) return by a tactic.

\holfour proofs are organized in theory files.
Each theory file contains definitions and statements of theorems together with
their proofs. Those theories and the contained proofs
are written
in the functional programming language \sml. To automate
proof search strategies a user can implement programming language functions
that correspond to more involved proofs.
Functions that correspond to backward proofs, called tactics, are combined with
each other with the help of
tacticals (functions that takes
tactics as arguments). Such a combination of tactics will be called a
\emph{proof script} when it
proves a theorem stated in a theory.

>>>>

\paragraph{Two ways of representing a formulas.}\todo{RK: Actually I don't know what two ways you mean...?}

\paragraph{Theories and script files.}
Formal developments in \holfour are organized into named theories, which are concretely implemented by \emph{script} files defining modules in the functional programming language \sml.
Each script file corresponds to a single theory, and contains definitions of types and constants as well as statements of theorems together with their proofs.
In practice, tactic-based proofs are written in an informally specified \emph{embedded domain-specific language}: the language consisting of pre-defined tactics and \emph{tacticals} (functions that operate on tactics).
However, the full power of \sml is always available for users to define their own tactics or combinations thereof.
%To automate proof search strategies a user can implement programming language functions that correspond to more involved proofs.
%Functions that correspond to backward proofs, called tactics, are combined with each other with the help of tacticals (functions that takes
%tactics as arguments).
%Such a combination of tactics will be called a \emph{proof script} when it proves a theorem stated in a theory.

\paragraph{Tactics in \holfour.}
Considering concrete implementation details now, a \emph{tactic} is a function that takes a goal (or proof obligation) and returns a list of goals together with a validation function.
\todo{flesh the below out}
Input of the prediction: goal If a tactic produces no goals then its input goal is solved.
Define tactical etc maybe import graphic that explain how tactic works form the
presentations.
mention proof obligations (use this word) return by a tactic.
